\newpage
\section{Conclusion}
\label{sec:conclusion}

This project was mostly successful in implementing a software simulation of a
taxi market where fare prices are chosen by a Q-Learner agent. 

The software fulfilled all of the core goals to the minimum specification, and
exceeded the minimum requirements in some areas. The software suffers from
several small implementation issues that have been clearly identified, and a
plan for fixing these issues was provided. While some problems were identified
with the software development approach that was followed, it was adequate and
proved beneficial overall.

The simulation experiment was successfully completed with twelve different
scenarios. It was found that having variable fare pricing results in
significantly larger profits to a taxi, confirming the project hypothesis.
Furthermore, it was made clear that the Q-Learner had been a reasonable choice
for controlling the taxi and it's fare pricing, as it showed a clear trend of
increasing profits over time.

However, the results additionally revealed an inconclusive profitability trend
in one of the intentionally challenging scenarios, suggesting that the
Q-Learner was not performing correctly. Although this was an isolated instance
of the problem, this leads to think that there may be a bug or a design
oversight in the software which needs further investigation in future.

Nevertheless, variable pricing proved to be more profitable than fixed pricing,
therefore opening future possibilities for the project's topic and software.
Possible future work includes fixing the known issues with the software,
experimenting with different reinforcement learning strategies or even
researching the wider social implications of a variable fare pricing approach.
Beyond the realm of taxis, it is worth considering to utilise variable pricing
and reinforcement learning for public transport in general.
