(15, 3200 w)

Has the student carried out an evaluation?

Does the student present the results of the evaluation clearly and in a logical
manner?

Does the student explain the problems and difficulties found?

Does the student demonstrate an understanding and interpretation of results and
their significance?

Is there any critical evaluation of the project relative to the achievements of
related works?

Does the student present a personal reflection of what has been achieved and
not achieved in the project?

Has the student suggested future work?


\subsection{Results}

\todo{open-source results}

\todo{list other hidden constants?}

The experiments and their analysis can be repeated by following the
instructions in User Manual in Appendix \ref{sec:user_manual}. 

\todo{rephrase this horrific text}
The result datasets can be found in the \texttt{standard} directory in the open
data set mentioned in \ref{sec:intro:openness}. All of the results used were
generated using the inputs in Table \ref{table:input_data}.

\begin{table}
\begin{tabular}{ | l | l | }
  \hline
  Parameter & Value \\ \hline
  Time Limit & 1 000 000 \\
  Road network & with 6 locations, distances between 1-5 \\
  Passengers' expected fare & 20 \\
  Taxi's variable price range & 5-100 (integers) \\
  Taxi's benchmark price & 20 \\
  \hline
\end{tabular}
\caption{
  Simulation inputs
  \label{table:input_data}
}
\end{table}

The simulation was additionally run for control purposes, varying one input
parameter at a time. These runs are summarised in Table
\ref{table:inputs:control}, displaying the parameter in question and its
changed value, as well as the directory in the open data source where the
results are located.

\begin{table}
\begin{tabular}{ | l | l | l | }
  \hline
  Parameter & Value & Result Directory \\ \hline
  Benchmark price & 15 & \texttt{lower\_benchmark} \\
  Benchmark price & 30 & \texttt{higher\_benchmark} \\
  Taxi's price range & 5 - 20 & \texttt{lower\_range} \\
  Taxi's price range & 20 - 100 & \texttt{higher\_range} \\
  Time limit & 50 000 & \texttt{limited\_time} \\
  \hline
\end{tabular}
\caption{
  Control parameter changes
  \label{table:inputs:control}
}
\end{table}


Run 1: Non-regulated price much more successful with when the fixed price
equals the expected price. non regulated profit = 1000965; fixed fare loss
-1547613


\todo{process data and diagrams}

ai profitability over time, see how much time it takes for it to become
profitable etc

look at how the prices charged change over time, if at all
