(15, 3200 w)

Is there evidence of sufficient background reading and knowledge of relevant
literature?

Is there evidence of a clear understanding of the project area/research topic
and the relevant concepts?

Is the literature study up to date and critically evaluated?

Has the student appropriately reviewed competing technologies and/or products
in the marketplace?

Has the student appropriately consulted users of the proposed system?


Pricing is one of the main problems in transportation due to its large social
impact, whether it be road tolls, bus prices or regulated taxi fares. One of
the most controversial topics in the taxi market is about whether market
regulation is necessary. There is no consensus on this question, and different
authors give contradictory opinions based both on theoretical studies and
factual real world research. The economics of transportation are covered in
Section \ref{sec:literature:taxis}.

The next part of background that needs covering is artificial intelligence and
reinforcement learning in particular. The various ways of modelling
reinforcement learning problems are investigated in Section
\ref{sec:literature:ai}.

Finally, related works are discussed in Section \ref{sec:literature:related},
spanning both artificial intelligence and transportation economics. A recent
trend with promising results for transport planning and pricing is usage of
microeconomic models based on individual agents, allowing variable pricing to
be used thus improving system efficiencies. In conjunction with this trend
software has been developed to simulate such agent- based scenarios, the most
notable of which is MATSim.
