\subsection{Related works}
\label{sec:literature:related}

\subsubsection{Studies}

\textcite{Emele2013pricing+rural} investigated an agent-based scenario for
variable public transport pricing where both passengers and transport providers
submit requirements and bids to an intermediary agent. Transport vehicles can
be shared by multiple passengers, and passengers have hard and soft
requirements, with soft requirements ordered by importance (although only the
first soft requirement is taken in account by this system). This paper
concluded that variable pricing results in lower fares and more served
passengers than a fixed pricing scenario.

\textcite{Neumann2011berlin} researched how top-down aggregate and activity-
based microscopic agent-based models can be used in Berlin. It was found that
the both types of models used are complementary and provide similar results
most of the time. This study used MATSim, a piece of software described in
detail in Section \ref{sec:literature:related:simulation}. Although this study
did not cover pricing in any way, it is worth noting that both bottom-up and
top-down approaches can provide interchangeable results.


\subsubsection{Traffic Simulation Software}
\label{sec:literature:related:simulation}

Historically the most important traffic simulation software products have been
TRANSIMS \parencite{Smith1995taxi+transims} and EMME
\parencite{Gao2010taxi+comparison}. TRANSIMS operates on aggregated data in a
top-down fashion, and is limited to certain software modules and specific
inputs operating, and does not support agents. TRANSIMS proved to be useful at
its time, but agent-based microsimulation software has been more popular
recently because of the richer supported functionality.
\parencite{Bernhardt2007taxi+agent}

EMME in its latest version 4 is a commercial software, and potentially the most
advanced according to the claims of its parent company. However, it is of
limited interest for this project as EMME is a commercial and closed software.
\parencite{Inro2014emme}

\textcite{Bernhardt2007taxi+agent} gave an overview of agent-based software for
traffic modelling, naming MATSim as the most useful of these. MATSim is the most
noteworthy agent-based simulation and in active development. It has very
extensive capabilities and modules. However, it is complex to use and extend.
\textcite{Gao2010taxi+comparison} claimed that MATSim and EMME/2 has similar
performance and even produce compatible outputs.

ITSUMO by \textcite{Silva2006itsumo} is more limited simulation software using
intelligent agents to model traffic. \textcite{Bazzan2009integrating}
integrated  MATSim and ITSUMO to produce rich large scale traffic simulations.
MATSim, ITSUMO and the integrated piece of software are all meant to be
extendible. Unfortunately none of them have in-built support for agent
interactions that involve prices.

MATSim is arguably the most advanced of these open-source software products. It
has a large codebase under active development, and its documentation is
fragmented \textcite{Matsim2012}. Extending MATSim is conceptually a good
alternative to implementing custom software for this project. However, the
effort required to fully investigate the complexities of MATSim and work with
an unfamiliar legacy codebase is likely infeasible for the project's time
frame.


\subsubsection{Traffic Modelling}

\textcite[78]{Bernhardt2007taxi+agent} cited Bonabeau(2002a) for the following
conditions when agent based modelling is appropriate:

\begin{quote}
\begin{itemize}
  \item When there is potential for emergent phenomena--that is, individual 
  behaviour is nonlinear and changes over time, and fluctuations are more 
  important than averages;
  \item When describing the system from the perspective of its constituent 
  units’ activities is more natural--that is, “activities are a more natural way
  of describing the system than processes”; and
  \item When the appropriate level of description or complexity is not known 
  ahead of time.
\end{itemize}
\end{quote}

Finally, if an agent-based approach has been deemed appropriate, modelling can
be started. To create models the following needs to be carefully defined: the
environment; agents with their types, attributes, allowable and initial values
for the attributes; agent interaction rules with each other and the
environment. \parencite{Bernhardt2007taxi+agent}
